Supplementary Materials

### 2024-02-06 supplementary_materials/supplementary_materials.Rmd
manuscript revisions

>>>>

```{r roses1}
#| fig.cap: "RepOrting standards for Systematic Evidence Syntheses (ROSES) flow diagram for review process of fecal indicator bacteria (FIB) best management practice (BMP) studies."
#| fig.pos: "H"
#| out.extra: ""
#| out.width: "80%"

knitr::include_graphics("../figures/roses_bac.pdf")

```{r roses2}
#| fig.cap: "RepOrting standards for Systematic Evidence Syntheses (ROSES) flow diagram for review process of nutrient and sediment best management practice (BMP) studies."
#| fig.pos: "H"
#| out.extra: ""
#| out.width: "80%"

knitr::include_graphics("../figures/roses_nut.pdf")
